\hrule\hrule\bigskip\bigskip A simple and efficient algorithm for computing approximate Nash equilibria in two-person zero-sum games with imcomplete information

### 2015-06-07 nips2015.tex
more

\subsection{Relaxing the conditions for equilibrium}
Let us first introduce the notion of $\epsilon$-subgradients. The idea
is to replace the usual optimality characterization ``$x$ optimal iff
$0 \in \partial f(x)$'' with ``$x$ approx optimal iff $0 \in
\partial_\epsilon f(x)$''. In fact, letting $\epsilon \rightarrow 0^+$,
$\partial f(x) = \partial_{0^+}f(x)$ will coincide with
subgradient of $f$ at $x$, namely $\{h\in X | f(z) \ge f(x) + \langle
h, z - x\rangle \forall z \in X\}$.

>>>>

\subsection{Relaxing the conditions for equilibrium}
Let us first introduce the notion of $\epsilon$-subgradients. The idea
is to replace the usual optimality characterization ``$x$ optimal iff
$0 \in \partial f(x)$'' with ``$x$ approx optimal iff $0 \in
\partial_\epsilon f(x)$''. In fact, letting $\epsilon \rightarrow 0^+$,
$\partial f(x) = \partial_{0^+}f(x)$ will coincide with
subgradient of $f$ at $x$.
